On the relation of the entanglement spectrum to the bulk polarization \\ DRAFT

### 2020-10-30 version2/draft.tex
Final lic version

In the application of our results to topological systems we have focused on systems with translational invariance, both clean and with disorder. In general spatially inhomogeneous systems, not necesseraly with disorder, the bulk-boundary correspondence can appear in more interesting ways, such as in the case of quasicrystals in 1D \cite{Lang2012,Kraus2012}, which show properties characteristic of 2D topological insulators. In these systems our results might be able to give more insight into the relation between bulk and boundary. Another extension of our work can be in the field of higher-order topological insulators, where some systems can be characterized by a physical generalization of the bulk polarization to higher dimensions \cite{Benalcazar2017,Kang2019}. Our results for 1D might be able to be generalized to higher dimensions as well.

>>>>

\emph{Outlook:} In the application of our results to topological systems in 1D we have focused on systems with translational invariance even though our results do not require it. For general spatially inhomogeneous systems the same bulk can present different boundaries such that the relation between bulk and boundary is not as straighforward as in the translational invariant case. Our results might be able to give more insight into this relation.

In the field of higher-order topological insulators some systems can be characterized by a physical generalization of the bulk polarization to higher dimensions \cite{Benalcazar2017,Kang2019}. There is an open question wether a formulation in terms of twisted boundary conditions can be obtained, in which case our results might be able to generalize to higher dimensions.
